---
title: "Reporte Qualminer"
author: "Grupo de Trabajo de Manejo de la Información"
date: "12/10/2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r librerias, include=FALSE}
#install.packages("shiny")
#install.packages("dplyr")
#install.packages("ggplot2")
#install.packages("tidyr")
#install.packages("tidyverse")
#install.packages("rgdal") #readOGR
#install.packages("RColorBrewer")
#install.packages("classInt")
#install.packages("sf")
#install.packages("classInt")
#install.packages("leaflet")
#install.packages("ggrepel")
#install.packages("openxlsx")
#install.packages("fs")
#install.packages("readxl")
#install.packages("gridExtra")
#install.packages("knitr")
#install.packages("plyr")
#install.packages("reshape2")

library("shiny")
library("dplyr")
library("ggplot2")
library("tidyr")
library("stringi")
library("rgdal") #readOGR
library("RColorBrewer")
library("classInt")
library("sf")
library("classInt")
library("leaflet")
library("ggrepel")
library("openxlsx")
library("fs")
library("readxl")
library("gridExtra")
library("knitr")
library("plyr")
library("reshape2")

##MAPA CANTONES
shp_ecu<-st_read("E:\\REPORTE\\Bases trabajar\\cantones\\cantones.shp")
#shp_ecu<-st_read("C:\\Users\\URGILESB\\OneDrive - UNHCR\\Documents\\Reporte Qualminer\\cantones\\cantones.shp")
shp_ecu=shp_ecu[shp_ecu$dpa_provin!=20,]
shp_ecu=shp_ecu[shp_ecu$dpa_provin!=90,]

##BASE MEDIOS DE VIDA
#cac<-read.xlsx("C:\\Users\\URGILESB\\OneDrive - UNHCR\\Documents\\Reporte Qualminer\\Bases trabajar\\2019_12 Medios de vida.xlsx")
cac<-read.xlsx("E:\\REPORTE\\Bases trabajar\\2019_12 Medios de vida.xlsx")

#names(cac)<-c("dpa_canton","dpa_descan","Acceso_certificaciones_laborales","Acercamiento_empresa_privada_empleabilidad","Capacitación_en_gastronomía","Capacitación_incubadora_negocios","Capacitación_manipulación_alimentos","Capacitaciones_cuidado_a_personas","Capacitaciones_gastronomía","Capital_semilla_mujeres","Capital_semilla_MdG","Capital_semilla_VBG","Cursos_gratuitos","Empleabilidad_primera_vez","Empleabilidad_seguimiento","Emprendimiento_primera_vez","Emprendimiento_seguimiento","Escuela_emprendimiento","Estudio_mercado_local","Excel.para_emprendedores","Feria_emprendimientos","Financiamiento_productivo","Huertos_familiares","Incidencia_legalización_títulos","Incidencia_procesos_capacitación","Incidencia_sistema_financiero","Proyecto_piloto_MIES_HIAS_ACNUR","Sensibilización_población_mh","Taller_emprendedores","Taller_educación_financiera","Taller_empleabilidad","Taller_ventas_positivas","Talleres_redes_sociales_marketing_digital","Trabajo_interagencial_estado_academia_sector_privado")

names(cac)<-c("dpa_canton","dpa_descan","Access_labor_certifications","Approach_private_company_employability","Training_gastronomy","Business_incubator_training","Food_Handling_Training","Care_for_people_training","Gastronomy_training","Seed_capital_to_women","MGD_seed_capital","VGB_seed_capital","Free_Courses","First_time_employability","Treceability_employability","First_time_entrepreneurship","Entrepreneurship_monitoring","Entrepreneurship_School","Local_market_study","Excel_for_entrepreneurs","Fair_entrepreneurship","Productive_financing","Family_relatives","Legalization_incident_titles","Incidence_for_training_processes","Financial_system_Incidence","MIES_HIAS_UNHCR_pilot_project","Sensitization_population_mh","Entrepreneurs_Workshop","Financial_education_workshop","Employability_Workshop","Positive_sales_workshop","Social_networking_digital_marketing_workshops","InterWork_state_APS")

#Union SHAPE format file with the excel base
shp_ecutot<-left_join(shp_ecu,cac,by= "dpa_canton")

##Acceso EDUACIÓN
ed1<-read.xlsx("E:\\REPORTE\\Bases trabajar\\2019_12_Acceso a la educación.xlsx",1)
names(ed1)<-c("dpa_canton","dpa_descan","Community_integration_activities(HIAS)","Dissemination_mechanisms_homologation_titles(HIAS)","Strengthening_children's_space(HIAS)","School_integration(HIAS)","School_stay(HIAS)","Promotion_rights_Day_girl(HIAS)","School_leveling_project(HIAS)","Community_projects(HIAS)","Reference_small_NNcases(HIAS)","Family_tracking(HIAS)","Regular_workshops_right_access(HIAS)","Interangencial_state_academy_Work(HIAS)","Sanitary_Infrastructure_Maintenance(NRC)","School_kits(OIM)")

ed3<-read.xlsx("E:\\REPORTE\\Bases trabajar\\2019_12_Acceso a la educación.xlsx",3)
names(ed3)<-c("dpa_canton","dpa_descan","ADRA","DE_Quitumbe","DE_LAgrio","MIES","RAOA_SUR","SigloXXI","UARTES","UNICEF","UTN","UE_Isaac_Acosta")


###WASH###
##INGLÉS
wash<-read.xlsx("E:\\REPORTE\\Bases trabajar\\2019_12_Wash.xlsx",4)

#ESPAÑOL
#wash<-read.xlsx("C:\\Users\\URGILESB\\OneDrive - UNHCR\\Documents\\Reporte Qualminer\\Bases trabajar\\2019_12_Wash.xlsx",5)
#El informe que se muestra a continuación se realizó con algunos registros de las actividades realizadas por los socios en el mes de octubre. Para ello se consideró medios de vida, acceso a la educación y wash.

#**MEDIOS DE VIDA**

#En Medios de subsistencia, HIAS ha sido un actor muy importante debido a las actividades que se han llevado a cabo en las diferentes ciudades del país donde se encuentran principalmente las oficinas y los socios, ya que han sido de vital ayuda.
#A continuación se muestran los mapas donde se han identificado las actividades que se han llevado a cabo con mayor frecuencia y las ciudades donde se realizaron.

#The report shown below was made with some records of the activities carried out by the partners in the month of October. This was considered Livelihoods, Access to Education and Wash.

#**LIVELIHOODS**

#In Livelihoods, UNHCR has been a very important actor because of the activities that have been carried out in the different cities of the country where offices and partners are mainly located, since they have been of vital help.
#Below are the maps where the activities that have been carried out most frequently have been identified and the cities where they were carried out.
```

The report shown below was made with some records of the activities carried out by the partners in the month of October. This was considered Livelihoods, Access to Education and Wash.

**LIVELIHOODS**

In Livelihoods, UNHCR has been a very important actor because of the activities that have been carried out in the different cities of the country where offices and partners are mainly located, since they have been of vital help.
Below are the maps where the activities that have been carried out most frequently have been identified and the cities where they were carried out.

```{r echo=FALSE}
a<-ggplot(shp_ecutot)+
  #geom_sf(aes(fill= Empleabilidad_primera_vez)) +
  geom_sf(aes(fill= First_time_employability)) +
  theme_bw()+theme(
    panel.background = element_rect(fill = "white", color="gray70"),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_line(colour = "white"),
    plot.title = element_text(size = 18, face = 'bold', colour = "white", hjust=0.5, vjust=0),
    axis.title.x = element_text(size = 12, vjust=-0.5),
    axis.title.y = element_text(size = 12, vjust=1),
    axis.text = element_text(size = 10),
    axis.ticks = element_line(colour = "white")
  )

b<-ggplot(shp_ecutot)+
  geom_sf(aes(fill= Treceability_employability)) +
  theme_bw()+theme(
    panel.background = element_rect(fill = "white", color="gray70"),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_line(colour = "white"),
    plot.title = element_text(size = 18, face = 'bold', colour = "white", hjust=0.5, vjust=0),
    axis.title.x = element_text(size = 12, vjust=-0.5),
    axis.title.y = element_text(size = 12, vjust=1),
    axis.text = element_text(size = 10),
    axis.ticks = element_line(colour = "white")
  )


c<-ggplot(shp_ecutot)+
  geom_sf(aes(fill= First_time_entrepreneurship)) +
  theme_bw()+theme(
    panel.background = element_rect(fill = "white", color="gray70"),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_line(colour = "white"),
    plot.title = element_text(size = 18, face = 'bold', colour = "white", hjust=0.5, vjust=0),
    axis.title.x = element_text(size = 12, vjust=-0.5),
    axis.title.y = element_text(size = 12, vjust=1),
    axis.text = element_text(size = 10),
    axis.ticks = element_line(colour = "white")
  )

d<-ggplot(shp_ecutot)+
  geom_sf(aes(fill= Entrepreneurship_monitoring)) +
  theme_bw()+theme(
    panel.background = element_rect(fill = "white", color="gray70"),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_line(colour = "white"),
    plot.title = element_text(size = 18, face = 'bold', colour = "white", hjust=0.5, vjust=0),
    axis.title.x = element_text(size = 12, vjust=-0.5),
    axis.title.y = element_text(size = 12, vjust=1),
    axis.text = element_text(size = 10),
    axis.ticks = element_line(colour = "white")
  )

grid.arrange(a,c)
grid.arrange(d,b)

#En este caso, las actividades que más se realizaron son "Empleabilidad por primera vez" en la ciudad de Cuenca, "Seguimiento de empleabilidad" en algunas ciudades como Esmeraldas, Guayaquil, Lago Agrio. , Quito, Santo Domingo y Tulcán, sin embargo, en las actividades "Emprendimiento por primera vez" y "Emprendimiento seguimiento", vemos que hay algunas ciudades donde se han llevado a cabo estas actividades.

#In this case, the activities that were carried out are "Employability for the first time" in the city of Cuenca, more of these activities were carried out, "Employability by repeatability" carried out for some cities such as Esmeraldas, Guayaquil, Lago Agrio, Quito, Santo Domingo and Tulcán, however, for "Entrepreneurship for the first time" and "Entrepreneurship monitoring" we see that there are some cities where these activities have been carried out.
```

In this case, the activities that were carried out are "Employability for the first time" in the city of Cuenca, more of these activities were carried out, "Employability by repeatability" carried out for some cities such as Esmeraldas, Guayaquil, Lago Agrio, Quito, Santo Domingo and Tulcán, however, for "Entrepreneurship for the first time" and "Entrepreneurship monitoring" we see that there are some cities where these activities have been carried out.

```{r echo=FALSE}
####OTRAS CATEGORÍAS
e<-ggplot(shp_ecutot)+
  geom_sf(aes(fill=Financial_system_Incidence)) +
  theme_bw()+theme(
    panel.background = element_rect(fill = "white", color="gray70"),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_line(colour = "white"),
    plot.title = element_text(size = 18, face = 'bold', colour = "white", hjust=0.5, vjust=0),
    axis.title.x = element_text(size = 12, vjust=-0.5),
    axis.title.y = element_text(size = 12, vjust=1),
    axis.text = element_text(size = 10),
    axis.ticks = element_line(colour = "white")
  )

f<-ggplot(shp_ecutot)+
  geom_sf(aes(fill= Entrepreneurs_Workshop)) +
  theme_bw()+theme(
    panel.background = element_rect(fill = "white", color="gray70"),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_line(colour = "white"),
    plot.title = element_text(size = 18, face = 'bold', colour = "white", hjust=0.5, vjust=0),
    axis.title.x = element_text(size = 12, vjust=-0.5),
    axis.title.y = element_text(size = 12, vjust=1),
    axis.text = element_text(size = 10),
    axis.ticks = element_line(colour = "white")
  )


g<-ggplot(shp_ecutot)+
  #geom_sf(aes(fill= Taller_educación_financiera)) +
  geom_sf(aes(fill= Financial_education_workshop)) +
  theme_bw()+theme(
    panel.background = element_rect(fill = "white", color="gray70"),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_line(colour = "white"),
    plot.title = element_text(size = 18, face = 'bold', colour = "white", hjust=0.5, vjust=0),
    axis.title.x = element_text(size = 12, vjust=-0.5),
    axis.title.y = element_text(size = 12, vjust=1),
    axis.text = element_text(size = 10),
    axis.ticks = element_line(colour = "white")
  )

h<-ggplot(shp_ecutot)+
  #geom_sf(aes(fill= Trabajo_interagencial_estado_academia_sector_privado)) +
  geom_sf(aes(fill= InterWork_state_APS)) +
  theme_bw()+theme(
    panel.background = element_rect(fill = "white", color="gray70"),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_line(colour = "white"),
    plot.title = element_text(size = 18, face = 'bold', colour = "white", hjust=0.5, vjust=0),
    axis.title.x = element_text(size = 12, vjust=-0.5),
    axis.title.y = element_text(size = 12, vjust=1),
    axis.text = element_text(size = 10),
    axis.ticks = element_line(colour = "white"))

grid.arrange(e,f)
grid.arrange(g,h)

#Otras de las principales actividades que se han llevado a cabo son "Incidencia en el sistema financiero" en Quito, principalmente también en otras ciudades del país, "Taller de emprendedores" en Ibarra y otras ciudades, "Taller de empleabilidad" en Tulcán y algunas ciudades y finalmente "El trabajo interagencial estado/academia/sector privado" se realizó principalmente en Cuenca, y también en Ibarra, Santo Domingo y Tulcán.

#**Acceso a Educación.**

#En Acceso a Educación se han llevado a cabo varias actividades; los socios que han participado son HIAS, NRC, IOM.
#A continuación se muestran las actividades realizadas en algunas ciudades del país, identificando cuántas actividades se llevaron a cabo en cada una de ellas.


#Other of the main activities that have been carried out are "Financial system impact" in Quito, mostly also in other cities of the country, "Entrepreneurs workshop" in Ibarra and other cities, "Employability workshop" in Tulcán and some cities and finally "Interagency work state academy private sector" was carried out mainly in Cuenca, and also in Ibarra, Santo Domingo and Tulcán. 

#**Access Education.**

#In Access Education several activities have been carried out, for a better visualization, in these the partners that have participated are HIAS, NRC, IOM. 
#The activities carried out in some cities of the country are shown below, identifying how many activities were carried out in each of them.
```


Other of the main activities that have been carried out are "Financial system impact" in Quito, mostly also in other cities of the country, "Entrepreneurs workshop" in Ibarra and other cities, "Employability workshop" in Tulcán and some cities and finally "Interagency work state academy private sector" was carried out mainly in Cuenca, and also in Ibarra, Santo Domingo and Tulcán. 

**Access Education.**

In Access Education several activities have been carried out, for a better visualization, in these the partners that have participated are HIAS, NRC, IOM. 
The activities carried out in some cities of the country are shown below, identifying how many activities were carried out in each of them.

```{r echo=FALSE}
ed1<-select(ed1,-dpa_canton)
ed1<-ed1[1:11,]

educt <- melt(ed1, id.vars = "dpa_descan")

ggplot(educt, aes(dpa_descan,variable)) +
  geom_tile(aes(fill = value), color = "white") +
  scale_fill_gradient(low = "white", high = "steelblue") +
  ylab("ACTIVIDADES") +
  xlab("CANTONES") +
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size = 12),
        plot.title = element_text(size=16),
        axis.title=element_text(size=14,face="bold"),
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(fill = "Número de Actividades")


#It can be seen that the activity for access to education that has been most carried out is Interagencial_state_academy_work, mainly in the city of Guayaquil, followed by Lago Agrio.

#One of the partners such as HIAS, when implementing some of the activities for access to education, has worked with some institutions in the education sector, then we will see with which institutions they have worked more.

#Se puede observar que la actividad de acceso a la educación que más se ha llevado a cabo es "Trabajo_interagencial estado/academia/sector privado", principalmente en la ciudad de Guayaquil, seguida de Lago Agrio.

#Uno de los socios, como HIAS, al implementar algunas de las actividades de acceso a la educación, ha trabajado con algunas instituciones del sector educativo, a continuación se puede ver con qué instituciones han trabajado más.
```

It can be seen that the activity for access to education that has been most carried out is Interagencial_state_academy_work, mainly in the city of Guayaquil, followed by Lago Agrio.

One of the partners such as HIAS, when implementing some of the activities for access to education, has worked with some institutions in the education sector, then we will see with which institutions they have worked more.


```{r echo=FALSE}
ed3c<-ed3[1:11,]
ed3c<-select(ed3c,-dpa_canton)
ed3c<-mutate(ed3c,PARTNER=c("HIAS","NONE","HIAS","HIAS/ OIM","HIAS","HIAS","HIAS",
                          "HIAS","HIAS","HIAS/NRC","NRC"))
ed3c<-ed3c%>%
  select(PARTNER,dpa_descan,ADRA,DE_Quitumbe,DE_LAgrio,MIES,RAOA_SUR,SigloXXI,UARTES,UNICEF,UTN,UE_Isaac_Acosta)

DT::renderDataTable(ed3c)
```


```{r echo=FALSE}
ed3<-select(ed3,-dpa_canton,-dpa_descan)
ed3<-ed3[1:11,]

par(cex.axis=0.45,cex.lab=0.5,cex.sub=0.7,las=1)
SE<-barplot(sort(colSums(ed3,na.rm = TRUE)),col=c("lavenderblush","lavenderblush","lavenderblush","lavenderblush","lavenderblush","lavenderblush","lavenderblush","pink","pink","indianred1") ,main = "",axes = F,)

```


**WASH**

Wash, we will have the information on the activities in a narrative way that were carried out, classified by city, partners and the number of times each of them has been carried out.

```{r echo=FALSE}

#En Wash, tendremos la información sobre las actividades de manera narrativa que se llevaron a cabo, clasificadas por ciudad, socios y el número de veces que se ha llevado a cabo cada una de ellas.
#Wash, we will have the information on the activities in a narrative way that were carried out, classified by city, partners and the number of times each of them has been carried out.
wash<-select(wash,-DPA_CANTON)
DT::renderDataTable(wash)

#Se puede ver que en algunas ciudades hay tres actividades, en algunas solo una y en otras ninguna.
#You can see that in some cities there are three activities, in some only one and in others none, but only once.
```

You can see that in some cities there are three activities, in some only one and in others none, but only once.

